---
title: "WQD7004-OCC3&RL: Group Assignment(Group 9)"
output:
  html_document:
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
    toc_depth: 4
    number_sections: yes
    theme: spacelab
  word_document:
    toc: yes
    toc_depth: '4'
  pdf_document:
    toc: yes
    toc_depth: '4'
editor_options:
  chunk_output_type: console
---

# Introduction

Airline satisfaction is a crucial aspect of the aviation industry as it directly impacts the loyalty and repeat business of customers. A dataset of airline satisfaction data collected from Kaggle will be analyzed in this report. We will examine the data and conduct various analyses to understand the behavior and satisfaction of passengers. It is hoped that the insights and conclusions from this analysis will enable airlines to improve their services and increase their passenger satisfaction.

The dataset can be found here: [Airline Passenger Satisfaction Dataset](https://www.kaggle.com/datasets/teejmahal20/airline-passenger-satisfaction)

# Objectives
1. To understand the main factor that affects the passenger satisfaction.
2. To understand the correlation between the services provided by Airline.
3. To understatnd the accuracy of classification model.

# Methodology
## Data Understanding

* Our dataset contains 24 distinct features and 103,904 entries, including information on various aspects of the flight experience, such as in-flight Wi-Fi service, online booking ease, gate location, food and drink, seat comfort, in-flight entertainment, on-board service, legroom, baggage handling, check-in service, cleanliness, as well as passenger demographics such as gender, age, and travel type. 

* A passenger's overall satisfaction with the flight is also included, along with information on departure and arrival delay times. 

* Additionally, the data is composed of categorical and numerical variables, which serves as a tool for understanding passenger behavior and their level of satisfaction. The data will be explored and cleaned before analysis to identify any potential issues.

### Libraries
```{r include = FALSE, warning = FALSE}
# check installed package
packages <- c("stringr", "data.table", "ggpubr", "tidyr", "ggrepel", 
              "GGally", "vip", "patchwork", "ggplot2", "dplyr", 
              "magrittr", "caret", "lattice","ggcorrplot", "devtools", 
              "caTools", "e1071", "class")
install.packages(setdiff(packages, rownames(installed.packages())), 
                 repos = "http://cran.us.r-project.org")
```

```{r echo = TRUE, warning = FALSE, message = FALSE, results = 'hide'}
# load library
library(ggcorrplot)
library(lattice)
library(stringr)
library(dplyr)
library(data.table)
library(ggplot2)
library(ggpubr)
library(tidyr)
library(ggrepel)
library(GGally)
library(vip)
library(patchwork)
library(magrittr)
library(caret)
library(devtools)
library(caTools)
library(party)
library(e1071)
library(class)
```

### Airline Passenger Satisfaction Dataset
The dataset is uncleaned by modifying and removing some values, as well as replacing with inaccurate data via Microsoft Excel. The modified dataset will be used to perform data cleaning later.
```{r echo = TRUE, warning = FALSE}
airline_df <- read.csv("Airline Passenger Satisfaction Dataset\\train_unclean.csv"
                       , header = TRUE
                       , stringsAsFactors = TRUE)
```
Dimension of the dataset
```{r echo = TRUE, warning = FALSE}
dim(airline_df)
```
First 5 rows in the dataset
```{r echo = TRUE, warning = FALSE}
head(airline_df)
```
Data Types for each attribute in the dataset
```{r echo = TRUE, warning = FALSE}
sapply(airline_df, class)
```
Summary of the dataset
```{r echo = TRUE, warning = FALSE}
summary(airline_df)
```

### Data Checking
The purpose of data checking is to ensure that the data gathered is accurate, consistent, and complete to perform reliable analysis in the later stage.  
**Check duplicate data using the id attribute (unique identifier)**
```{r echo = TRUE, warning = FALSE}
dim(airline_df[duplicated(airline_df$id),])[1]
```
**Check missing values in each attribute**
```{r echo = TRUE, warning = FALSE}
colSums(is.na(airline_df))
```
**Check distinct values in each nominal attribute**
```{r echo = TRUE, warning = FALSE}
levels(airline_df$Gender)
levels(airline_df$Customer.Type)
levels(airline_df$Type.of.Travel)
levels(airline_df$Class)
```

## Data Cleaning
### Nominal Data
**Gender**  
Convert Gender into proper case
```{r echo = TRUE, warning = FALSE}
airline_df$Gender.C <-
  as.factor(str_to_title(airline_df$Gender))
levels(airline_df$Gender.C)
```
**Customer Type**  
Convert Customer Type into proper case
```{r echo = TRUE, warning = FALSE}
airline_df$Customer.Type.C <- 
  as.factor(str_to_title(airline_df$Customer.Type))
levels(airline_df$Customer.Type.C)
```
**Type of Travel**  
Correct Type of Travel categories
```{r echo = TRUE, warning = FALSE}
airline_df$Type.of.Travel.C <- 
  ifelse(grepl('^b', airline_df$Type.of.Travel, ignore.case = TRUE), 
         "Business Travel",
         "Personal Travel")
airline_df$Type.of.Travel.C <- as.factor(airline_df$Type.of.Travel.C)
levels(airline_df$Type.of.Travel.C)
```
**Class**  
Correct Class categories
```{r echo = TRUE, warning = FALSE}
airline_df$Class.C <- 
  ifelse(grepl('^b', airline_df$Class, ignore.case = TRUE), 
         "Business", "Eco")
airline_df$Class.C <- as.factor(airline_df$Class.C)
levels(airline_df$Class.C)
```

### Ordinal Data
All attributes with rating are considered as ordinal data.  
**Inflight Wifi Service**  
Replace ratings above 5 as NA (missing values) then impute missing values with mean excluding 0
```{r echo = TRUE, warning = FALSE}
airline_df$Inflight.wifi.service.C <- airline_df$Inflight.wifi.service
airline_df$Inflight.wifi.service.C[airline_df$Inflight.wifi.service.C > 5] <- NA
airline_df$Inflight.wifi.service.C[is.na(airline_df$Inflight.wifi.service.C)] <-
  mean(airline_df$Inflight.wifi.service.C
       [airline_df$Inflight.wifi.service.C > 0]
       , na.rm = TRUE
       )
```
Convert to integer
```{r echo = TRUE, warning = FALSE}
airline_df$Inflight.wifi.service.C <- 
  round(airline_df$Inflight.wifi.service.C)
```
**Food and Drink**  
Replace ratings above 5 as NA (missing values) then impute missing values with mean excluding 0  
```{r echo = TRUE, warning = FALSE}
airline_df$Food.and.drink.C <- airline_df$Food.and.drink
airline_df$Food.and.drink.C[airline_df$Food.and.drink.C > 5] <- NA
airline_df$Food.and.drink.C[is.na(airline_df$Food.and.drink.C)] <-
  mean(airline_df$Food.and.drink.C
       [airline_df$Food.and.drink.C > 0]
       , na.rm = TRUE
       )
```
Convert to integer
```{r echo = TRUE, warning = FALSE}
airline_df$Food.and.drink.C <- 
  round(airline_df$Food.and.drink.C)
```
**Seat Comfort**  
Replace ratings above 5 as NA (missing values) then impute missing values with mean excluding 0
```{r echo = TRUE, warning = FALSE}
airline_df$Seat.comfort.C <- airline_df$Seat.comfort
airline_df$Seat.comfort.C[airline_df$Seat.comfort.C > 5] <- NA
airline_df$Seat.comfort.C[is.na(airline_df$Seat.comfort.C)] <-
  mean(airline_df$Seat.comfort.C
       [airline_df$Seat.comfort.C > 0]
       , na.rm = TRUE
       )
```
Convert to integer
```{r echo = TRUE, warning = FALSE}
# convert to integer
airline_df$Seat.comfort.C <- 
  round(airline_df$Seat.comfort.C)
```
**All attributes with ratings**  
Convert all ratings attributes to ordinal data
```{r echo = TRUE, warning = FALSE}
ratings <- c("Inflight.wifi.service.C", "Food.and.drink.C", "Seat.comfort.C",
          "Departure.Arrival.time.convenient",	"Ease.of.Online.booking",
          "Gate.location", "Online.boarding", "Inflight.entertainment",
          "On.board.service",	"Leg.room.service",	"Baggage.handling",
          "Checkin.service",	"Inflight.service",	"Cleanliness"
          )
airline_df[ratings] <- lapply(airline_df[ratings], 
                              factor, 
                              levels=c(0, 1, 2, 3, 4, 5)
                              )
```

### Continuous Data
**Departure & Arrival Delay in minutes**  
Replace NA with 0
```{r echo = TRUE, warning = FALSE}
delay_cols <- c("Departure.Delay.in.Minutes", "Arrival.Delay.in.Minutes")
airline_df[delay_cols][is.na(airline_df[delay_cols])] <- 0
```

### Tidy Up
```{r echo = TRUE, warning = FALSE}
# rearrange columns
col_order <- c("X", "id", "Gender", "Gender.C", "Customer.Type",
               "Customer.Type.C", "Age", "Type.of.Travel", "Type.of.Travel.C",
               "Class", "Class.C","Flight.Distance", "Inflight.wifi.service", 
               "Inflight.wifi.service.C", "Departure.Arrival.time.convenient",	
               "Ease.of.Online.booking", "Gate.location", "Food.and.drink",
               "Food.and.drink.C", "Online.boarding", "Seat.comfort", 
               "Seat.comfort.C", "Inflight.entertainment", "On.board.service",	
               "Leg.room.service", "Baggage.handling", "Checkin.service",	
               "Inflight.service",	"Cleanliness", "Departure.Delay.in.Minutes",
               "Arrival.Delay.in.Minutes", "satisfaction"
               )
airline_df <- airline_df[, col_order]

# drop columns
drop_col <- c("Gender", "Customer.Type", "Type.of.Travel", "Class",
              "Inflight.wifi.service", "Food.and.drink", "Seat.comfort")
airline_df[, drop_col] <- list(NULL)

# rename columns
old_colnames <- c("Gender.C", "Customer.Type.C", "Type.of.Travel.C", "Class.C", 
                  "Inflight.wifi.service.C", "Food.and.drink.C", "Seat.comfort.C"
                  )
new_colnames <- drop_col
setnames(airline_df, old = old_colnames, new = new_colnames)

# drop "X" column
airline_df[, "X"] <- list(NULL)
```

## Exploratory Data Analysis (EDA)

### Overview
In this section, we will walk through an overall view of the airline satisfaction dataset, by customer demographics and service ratings.
```{r include = FALSE, warning = FALSE}
# Summarize table for visualization
# Customer Gender
cs_gender_df <- airline_df %>%
  group_by(Gender) %>%
  summarise(counts = n())%>% 
  mutate(perc = counts / sum(counts)) %>% 
  arrange(perc) %>%
  mutate(labels = scales::percent(perc))

# Customer type
cs_type_df <- airline_df %>%
  group_by(Customer.Type) %>%
  summarise(counts = n()) %>% 
  mutate(perc = counts / sum(counts)) %>% 
  arrange(perc) %>%
  mutate(labels = scales::percent(perc))

# Type of Travel
type_travel_df <- airline_df %>%
  group_by(Type.of.Travel) %>%
  summarise(counts = n()) %>% 
  mutate(perc = counts / sum(counts)) %>% 
  arrange(perc) %>%
  mutate(labels = scales::percent(perc))

# Class
class_df <- airline_df %>%
  group_by(Class) %>%
  summarise(counts = n()) %>% 
  mutate(perc = counts / sum(counts)) %>% 
  arrange(perc) %>%
  mutate(labels = scales::percent(perc))

# Customer Type by ratings in each factors
cs_type_ratings_df <- airline_df[c(3,8:21)]
cs_type_ratings_df <- 
  cs_type_ratings_df %>%
  pivot_longer(-c(Customer.Type),
               names_to = "services",
               values_to = "ratings")  %>%
  group_by(Customer.Type, services, ratings) %>%
  summarise(counts = n())

# Ratings in each factors
ratings_df <-
  cs_type_ratings_df %>%
  group_by(services, ratings) %>%
  summarise(freq = sum(counts))
```

#### Customers
Below graphs represent an overview of the passengers demographics and characteristics, which will be used in further analysis.  

**Customer Gender**  
```{r echo = FALSE, warning = FALSE, fig.height = 4}
# Gender Pie Chart
cs_gender_g <- 
  ggplot(cs_gender_df, 
         aes(x = "",
             y = perc, 
             fill = Gender)) + 
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y", start = 0) +
  guides(fill=guide_legend(title="Gender")) +
  geom_text(aes(label = labels), 
            position = position_stack(vjust = 0.5),
            show.legend = FALSE) +
  theme(plot.title = element_text(hjust = 1.0)) +
  scale_fill_brewer(palette="PRGn") +
  # labs(title = "Customer Gender") +
  theme_void()
cs_gender_g
```

As seen in the pie chart, the distribution of genders among the passenger population is relatively balanced, with 50.7% of the passengers being male and 49.3% of the passengers being female. The slight difference of 1.4% between the two indicates that the data is not skewed towards one gender, allowing for a fair representation of both male and female passengers.
  
**Customer Age**  
```{r echo = FALSE, warning = FALSE, fig.height = 4}
# Age Density Graph
cs_age_g <- 
  ggplot(data = airline_df, 
         aes( x = Age)
         ) + 
  geom_density(fill="navy blue", color="black", alpha=0.75) +
  labs(x = "Age", 
       y = "") + 
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_fill_brewer(palette="Spectral")
cs_age_g
```

The age distribution of the passenger population shows a clear pattern of increasing numbers as age increases, peaking in the twenties range. The number then drops slightly in the thirties age range, before climbing back up to the highest peak in the forties. From there, the number of passengers gradually decreases as age increases. This pattern is clearly visible in the graph, providing an overall picture of the age distribution among the passenger population.

**Customer Type**  
```{r echo = FALSE, warning = FALSE, fig.height = 4}
# customer type
cs_type_g <- 
  ggplot(cs_type_df, 
         aes(x = "",
             y = perc, 
             fill = Customer.Type)) + 
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y", start = 0) +
  guides(fill=guide_legend(title="Customer Type")) +
  geom_text(aes(label = labels), 
            position = position_stack(vjust = 0.5),
            show.legend = FALSE) +
  theme(plot.title = element_text(hjust = 1.0)) +
  scale_fill_brewer(palette="Spectral") +
  # labs(title = "Customer Type") +
  theme_void()
cs_type_g        
```

It can be observed that 18% of the customers are disloyal and 82% are loyal. This indicates that most of the customers have a history of repeat business with the company and can inform strategies to retain and attract loyal customers.

**Travel Type**  
```{r echo = FALSE, warning = FALSE, fig.height = 4}
# Type of Travel
type_travel_g <- 
  ggplot(type_travel_df, 
         aes(x = "",
             y = perc, 
             fill = Type.of.Travel)) + 
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y", start = 0) +
  guides(fill=guide_legend(title="Type of Travel")) +
  geom_text(aes(label = labels), 
            position = position_stack(vjust = 0.5),
            show.legend = FALSE) +
  theme(plot.title = element_text(hjust = 1.0)) +
  scale_fill_brewer(palette="Spectral") +
  # labs(title = "Customer Travel Type") +
  theme_void()
type_travel_g
```

Additionally, the data shows that 69% of the customers are traveling for business purposes and 31% are traveling for personal reasons. This can provide insight into the type of customers the company is serving and can inform marketing and sales efforts to specific segments of the customer base.

**Flight Class**  
```{r echo = FALSE, warning = FALSE, fig.height = 4}
# Class
class_g <- 
  ggplot(class_df, 
         aes(x = "",
             y = perc, 
             fill = Class)) + 
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y", start = 0) +
  guides(fill=guide_legend(title="Class")) +
  geom_text(aes(label = labels), 
            position = position_stack(vjust = 0.5),
            show.legend = FALSE) +
  theme(plot.title = element_text(hjust = 1.0)) +
  scale_fill_brewer(palette="Spectral") +
  # labs(title = "Flight Class") +
  theme_void()
class_g
```

Lastly, regarding flight class, the data indicates that 47.8% of the customers are traveling in business class, 52.2% in economy class. This information can be used to understand the type of customers that are traveling in different classes, adjust pricing and inventory management strategies, and understand the revenue generated from different classes of customers.

**Flight Arrival & Delay in Minutes**  

* Based on the box plot below, we can conclude that both arrival and departure delay mostly fall in the region of 0 minute to 10 minutes and with less amount of delay more than 10 minutes. Both delay are comparable to each other also.

```{r echo = FALSE, warning = FALSE, fig.height = 4}
# Departure Delay in Minutes
departure_delay_g <-
  ggplot(airline_df, 
         aes(x = "",
             y = Departure.Delay.in.Minutes)) + 
  geom_boxplot(width = 0.1, color = "black", alpha = 0.2) +
  coord_cartesian(ylim =  c(0, 50)) +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(title = "Departure Delay in Minutes", 
       x = "Departure Delay in Minutes",
       y = "") + 
  scale_fill_brewer(palette="Spectral")

# Arrival Delay in Minutes
arrival_delay_g <-
  ggplot(airline_df, 
         aes(x = "",
             y = Arrival.Delay.in.Minutes)) + 
  geom_boxplot(width = 0.1, color = "black", alpha = 0.2) +
  coord_cartesian(ylim =  c(0, 50)) +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(title = "Arrival Delay in Minutes", 
       x = "Arrival Delay in Minutes",
       y = "") + 
  scale_fill_brewer(palette="Spectral")
ggarrange(departure_delay_g, arrival_delay_g, ncol = 2)
```  

Overall, the data gives valuable insights into the customer base and can be used to inform business decisions and improve customer satisfaction. It allows the Airlines to understand the characteristics of their customers, such as loyalty, travel type and flight class, and use it to tailor their services and attract more customers.

#### Service Ratings
```{r echo = FALSE, warning = FALSE, fig.height = 20}
ratings_g <- 
  ggplot(ratings_df, 
         aes(x = ratings,
             y = freq, 
             fill = ratings)) + 
  geom_bar(stat='identity', position = "dodge") +
  labs(title = "Ratings in each services",
       x = "Ratings",
       y = "") + 
  theme(plot.title = element_text(hjust = 0.5)) +
  facet_grid(services ~ .) +
  scale_fill_brewer(palette="Spectral")
ratings_g
```

**(Pending interpretation)**  

---
Now, we will perform analysis from different perspectives, such as customer age, customer gender, customer type, travel type and flight class.

### Customer Age

**(Pending TONY's interpretation)**  

```{r include = FALSE, warning = FALSE}
Age_1 <- ggplot(airline_df, aes(Age, fill = satisfaction)) + geom_density(alpha = 0.5) + labs(title = "Age across Type of Travel", colour = "Type.of.Travel", y = "Number of Airline Passengers", x = "Type of Travel")+ 
  theme(axis.text = element_text(size = 5)) + theme(axis.title = element_text(size = 5)) + theme(plot.title = element_text(size = 7)) +
  theme(legend.text = element_text(size = 5))+ theme(legend.title = element_text(size = 5))+ theme(legend.key.height= unit(0.5, 'cm'),
                                                                                                   legend.key.width= unit(0.5, 'cm'))
Age_1
```

### Customer Gender

```{r include = FALSE, warning = FALSE}
#2a customer gender by customer type- table
cs_gender_cust_type_df <- airline_df %>%
  group_by(Gender, Customer.Type) %>%
  summarise(counts = n())

#3a customer gender by customer type and type of travel- table
cs_gender_cust_type_travel_df <- airline_df %>%
  group_by(Gender, Customer.Type, Type.of.Travel) %>%
  summarise(counts = n())

#4a customer gender by type of travel and class- table
cs_gender_travel_class_df <- airline_df %>%
  group_by(Gender, Type.of.Travel, Class) %>%
  summarise(counts = n())

#5a Create age group
airline_age_df <- airline_df
airline_age_df["age_group"] <- 
  cut(airline_age_df$Age, c(0, 10, 20, 30, 40, 50, 60, 70, 80, Inf),
  c("0-10", "11-20", "21-30","31-40","41-50","51-60","61-70","71-80", ">80"),
  include.lowest=TRUE)

#5b customer gender by age group and customer type- table
cs_gender_age_type_df <- airline_age_df %>%
  group_by(Gender, age_group, Customer.Type) %>%
  summarise(counts = n())

#6b customer gender by satisfaction- table
cs_gender_satisfied_df <- airline_df %>%
  group_by(Gender, satisfaction) %>%
  summarise(counts = n())

#6d customer gender by age group and satisfaction- table
cs_gender_age_satisfied_df <- airline_age_df %>%
  group_by(Gender, age_group, satisfaction) %>%
  summarise(counts = n())
```

```{r echo = FALSE, warning = FALSE}

#2b customer gender by customer type- graph
# Disloyal customer comprises of 20% of the whole dataset, of which 19% of female customers are disloyal, i.e. 2 % higher than male customers.
cs_gender_cust_type_g <- 
  ggplot(cs_gender_cust_type_df, 
         aes(x = Customer.Type,
             y = counts)) + 
  geom_bar(stat='identity', position = "dodge") +
  labs(x = "Customer Type", y = "Frequency") + 
  facet_wrap(~Gender) +
  scale_fill_brewer(palette="Spectral")+ 
  ggtitle("Customer Type by Gender in Train Dataset")
cs_gender_cust_type_g

#3b customer gender by customer type and type of travel- graph
#From the customer type, it is observed that almost all the disloyal customers came from business travel(99%), regardless of the gender.
cs_gender_cust_type_travel_g <- 
  ggplot(cs_gender_cust_type_travel_df, 
         aes(x = Customer.Type,
             y = counts, 
             fill = Type.of.Travel)) + 
  geom_bar(stat='identity', position = "dodge") +
  labs(x = "Customer.Type", y = "Frequency") + 
  facet_wrap(~Gender) +
  scale_fill_brewer(palette="Spectral")+ 
  ggtitle("Customer Type by Gender and Travel Type in Train Dataset")
cs_gender_cust_type_travel_g

#4b customer type by type of travel and class- graph
cs_gender_travel_class_g <- 
  ggplot(cs_gender_travel_class_df, 
         aes(x = Type.of.Travel,
             y = counts, 
             fill = Class)) + 
  geom_bar(stat='identity', position = "dodge") +
  labs(x = "Type of Travel", y = "Frequency") + 
  facet_wrap(~Gender) +
  scale_fill_brewer(palette="Spectral")+ 
  ggtitle("Customer Type by Travel Type and Class in Train Dataset")
cs_gender_travel_class_g

#5c customer gender by age group and customer type- graph
cs_gender_age_type_g <- 
  ggplot(cs_gender_age_type_df, 
         aes(x = age_group,
             y = counts,
             fill = Customer.Type)) + 
  geom_bar(stat='identity', position = "dodge") +
  labs(x = "age_group", y = "Frequency") + 
  facet_wrap(~Gender) +
  scale_fill_brewer(palette="Spectral")+ 
  ggtitle("Customer Type by Gender and Age Group in Train Dataset")
cs_gender_age_type_g

#6a Satisfaction count graph
#57% of the whole datasets comprises of neutral or dissatisfied customers, regardless of gender.
satisfaction_count <- airline_df %>% 
  count(satisfaction) %>% 
  ggplot(aes(x = satisfaction, y = n, fill = satisfaction)) +
  geom_bar(stat = "identity", colour = "black", alpha = 0.75) +
  geom_text(aes(label = n), 
                position=position_dodge(width=0.9), 
                vjust=-0.5) + 
  ylim(0, 60000) + 
  labs(y = "Count") + 
  scale_fill_brewer(palette="Spectral") + 
  ggtitle("Satisfaction variable in Train Dataset")
satisfaction_count
  
#6c customer gender by satisfaction- graph
cs_gender_satisfied_g <- 
  ggplot(cs_gender_satisfied_df, 
         aes(x = satisfaction,
             y = counts)) + 
  geom_bar(stat='identity', position = "dodge") +
  labs(x = "satisfaction", y = "Frequency") + 
  facet_wrap(~Gender) +
  scale_fill_brewer(palette="Spectral") + 
  ggtitle("Satisfaction by Gender in Train Dataset")
cs_gender_satisfied_g
  
#6e customer gender by age group and satisfaction- graph 
#Most of the disloyal customers aged between 21-30, followed by 31-40 age group. Possible reason is that people of younger adults are more inclined in trying different airlines that offers good deals. 
cs_gender_age_satisfied_g <- 
  ggplot(cs_gender_age_satisfied_df, 
         aes(x = satisfaction,
             y = counts,
             fill = age_group)) + 
  geom_bar(stat='identity', position = "dodge") +
  labs(x = "satisfaction", y = "Frequency") + 
  facet_wrap(~Gender) +
  scale_fill_brewer(palette="Spectral") + 
  ggtitle("Satisfaction by Gender and Age Group in Train Dataset")
cs_gender_age_satisfied_g

# Inflight.wifi.service across Gender
service1_g <- ggplot(airline_df, aes(Inflight.wifi.service, colour = Gender, fill = Gender)) + geom_bar(position = "dodge") + scale_fill_manual(values=c("#9933FF","#33FFFF"))+
  labs(title = "Inflight.wifi.service vs Gender", colour = "Gender")+ 
  theme(axis.text = element_text(size = 5)) + 
  theme(axis.title = element_text(size = 5)) +
  theme(plot.title = element_text(size = 5)) +
  theme(legend.text = element_text(size = 5))+
  theme(legend.title = element_text(size = 5)) 
service1_g
# Departure.Arrival.time.convenient across Gender
service2_g <- ggplot(airline_df, aes(Departure.Arrival.time.convenient, colour = Gender, fill = Gender)) + geom_bar(position = "dodge")+ scale_fill_manual(values=c("#9933FF","#33FFFF"))+ 
  labs(title = "Departure.Arrival.time.convenient across Gender", colour = "Gender")+ 
  theme(axis.text = element_text(size = 5)) + 
  theme(axis.title = element_text(size = 5)) +
  theme(plot.title = element_text(size = 5)) +
  theme(legend.text = element_text(size = 5))+
  theme(legend.title = element_text(size = 5)) 
service2_g
# Ease.of.Online.booking across Gender
service3_g <- ggplot(airline_df, aes(Ease.of.Online.booking, colour = Gender, fill = Gender)) + geom_bar(position = "dodge") + scale_fill_manual(values=c("#9933FF","#33FFFF"))+ 
  labs(title = "Ease.of.Online.booking across Type of Travel", colour = "Gender")+ 
  theme(axis.text = element_text(size = 5)) + 
  theme(axis.title = element_text(size = 5)) +
  theme(plot.title = element_text(size = 5)) +
  theme(legend.text = element_text(size = 5))+
  theme(legend.title = element_text(size = 5)) 
service3_g
# Gate.location across Gender
service4_g <- ggplot(airline_df, aes(Gate.location, colour = Gender, fill = Gender)) + geom_bar(position = "dodge") + scale_fill_manual(values=c("#9933FF","#33FFFF"))+ 
  labs(title = "Gate.location across Gender", colour = "Gender")+ 
  theme(axis.text = element_text(size = 5)) + 
  theme(axis.title = element_text(size = 5)) +
  theme(plot.title = element_text(size = 5)) +
  theme(legend.text = element_text(size = 5))+
  theme(legend.title = element_text(size = 5)) 
service4_g
# Food.and.Drink across Gender
service0_g <- ggplot(airline_df, aes(Food.and.drink, colour = Gender, fill = Gender)) + geom_bar(position = "dodge") + scale_fill_manual(values=c("#9933FF","#33FFFF"))+ 
  labs(title = "Gate.location across Gender", colour = "Gender")+ 
  theme(axis.text = element_text(size = 5)) + 
  theme(axis.title = element_text(size = 5)) +
  theme(plot.title = element_text(size = 5)) +
  theme(legend.text = element_text(size = 5))+
  theme(legend.title = element_text(size = 5)) 
service0_g
# Online.boarding across Gender
#In comparison, female customers are more satisfied in the online boarding service than male customers as most of the ratings are above 3 ratings.
service5_g <- ggplot(airline_df, aes(Online.boarding, colour = Gender, fill = Gender)) + geom_bar(position = "dodge") + scale_fill_manual(values=c("#9933FF","#33FFFF"))+ 
  labs(title = "Online.boarding across Gender", colour = "Gender")+ 
  theme(axis.text = element_text(size = 5)) + 
  theme(axis.title = element_text(size = 5)) +
  theme(plot.title = element_text(size = 5)) +
  theme(legend.text = element_text(size = 5))+
  theme(legend.title = element_text(size = 5)) 
service5_g
# Seat.comfort across Gender
#In comparison, female customers are more satisfied in the seat comfort aspect than male customers as most of the ratings are above 3 ratings.
service6_g <- ggplot(airline_df, aes(Seat.comfort, colour = Gender, fill = Gender)) + geom_bar(position = "dodge") + scale_fill_manual(values=c("#9933FF","#33FFFF"))+ 
  labs(title = "Seat.comfort across Gender", colour = "Gender")+ 
  theme(axis.text = element_text(size = 5)) + 
  theme(axis.title = element_text(size = 5)) +
  theme(plot.title = element_text(size = 5)) +
  theme(legend.text = element_text(size = 5))+
  theme(legend.title = element_text(size = 5)) 
service6_g
# Inflight.entertainment across Gender
service7_g <- ggplot(airline_df, aes(Inflight.entertainment, colour = Gender, fill = Gender)) + geom_bar(position = "dodge") + scale_fill_manual(values=c("#9933FF","#33FFFF"))+
  labs(title = "Inflight.entertainment across Gender", colour = "Gender")+ 
  theme(axis.text = element_text(size = 5)) + 
  theme(axis.title = element_text(size = 5)) +
  theme(plot.title = element_text(size = 5)) +
  theme(legend.text = element_text(size = 5))+
  theme(legend.title = element_text(size = 5)) 
service7_g
# On.board.service across Gender
service8_g <- ggplot(airline_df, aes(On.board.service, colour = Gender, fill = Gender)) + geom_bar(position = "dodge") + scale_fill_manual(values=c("#9933FF","#33FFFF"))+ 
  labs(title = "On.board.service across Gender", colour = "Gender")+
  theme(axis.text = element_text(size = 5)) + 
  theme(axis.title = element_text(size = 5)) +
  theme(plot.title = element_text(size = 5)) +
  theme(legend.text = element_text(size = 5))+
  theme(legend.title = element_text(size = 5)) 
service8_g
# Leg.room.service across Gender
#Female passengers are more dissatisfied with the lower rating given to leg room service, as compared to male passengers.
service9_g <- ggplot(airline_df, aes(Leg.room.service, colour = Gender, fill = Gender)) + geom_bar(position = "dodge") + scale_fill_manual(values=c("#9933FF","#33FFFF"))+
  labs(title = "Leg.room.service across Gender", colour = "Gender")+ 
  theme(axis.text = element_text(size = 5)) + 
  theme(axis.title = element_text(size = 5)) +
  theme(plot.title = element_text(size = 5)) +
  theme(legend.text = element_text(size = 5))+
  theme(legend.title = element_text(size = 5)) 
service9_g
# Baggage.handling across Gender
#Female passengers are more dissatisfied in baggage handling service than male passengers. Possible reason is that female passengers carry cosmetic products that are fragile items and thus negligence in handling with care cause them to be unhappy with the service.
service10_g <- ggplot(airline_df, aes(Baggage.handling, colour = Gender, fill = Gender)) + geom_bar(position = "dodge") + scale_fill_manual(values=c("#9933FF","#33FFFF"))+ 
  labs(title = "Baggage.handling across Gender", colour = "Gender")+ 
  theme(axis.text = element_text(size = 5)) + 
  theme(axis.title = element_text(size = 5)) +
  theme(plot.title = element_text(size = 5)) +
  theme(legend.text = element_text(size = 5))+
  theme(legend.title = element_text(size = 5)) 
service10_g
# Checkin.service across Gender
service11_g <- ggplot(airline_df, aes(Checkin.service, colour = Gender, fill = Gender)) + geom_bar(position = "dodge") + scale_fill_manual(values=c("#9933FF","#33FFFF"))+ 
  labs(title = "Checkin.service across Gender", colour = "Gender")+ 
  theme(axis.text = element_text(size = 5)) + 
  theme(axis.title = element_text(size = 5)) +
  theme(plot.title = element_text(size = 5)) +
  theme(legend.text = element_text(size = 5))+
  theme(legend.title = element_text(size = 5)) 
service11_g
# Inflight.service across Gender
#Female passengers are more dissatisfied in inflight service than male passengers.
service12_g <- ggplot(airline_df, aes(Inflight.service, colour = Gender, fill = Gender)) + geom_bar(position = "dodge") + scale_fill_manual(values=c("#9933FF","#33FFFF"))+ 
  labs(title = "Inflight.service across Gender", colour = "Gender")+ 
  theme(axis.text = element_text(size = 5)) + 
  theme(axis.title = element_text(size = 5)) +
  theme(plot.title = element_text(size = 5)) +
  theme(legend.text = element_text(size = 5))+
  theme(legend.title = element_text(size = 5)) 
service12_g
# Cleanliness across Gender
service13_g <- ggplot(airline_df, aes(Cleanliness, colour = Gender, fill = Gender)) + geom_bar(position = "dodge") + scale_fill_manual(values=c("#9933FF","#33FFFF"))+ 
  labs(title = "Cleanliness across Gender", colour = "Gender")+ 
  theme(axis.text = element_text(size = 5)) + 
  theme(axis.title = element_text(size = 5)) +
  theme(plot.title = element_text(size = 5)) +
  theme(legend.text = element_text(size = 5))+
  theme(legend.title = element_text(size = 5)) 
service13_g
# Departure.Delay.in.Minutes across Gender
service14_g <-
  ggplot(airline_df, 
         aes(x = Gender,
             y = Departure.Delay.in.Minutes,
             fill = Gender,
             color = Gender)) + 
  geom_violin(width = 0.3, position = position_dodge())+
  geom_boxplot(width = 0.1, color = "black", alpha = 0.2) +
  labs(title = "Departure.Delay.in.Minutes by Gender", 
       x = "Gender",
       y = "Departure.Delay.in.Minutes") + 
  scale_fill_brewer(palette="Spectral")
service14_g
```

### Customer Type

```{r include = FALSE, warning = FALSE}
# customer type by type of travel and class
cs_type_travel_class_df <- airline_df %>%
  group_by(Customer.Type, Type.of.Travel, Class) %>%
  summarise(counts = n())

# customer type by satisfaction
cs_type_satisfaction_df <- airline_df %>%
  group_by(Customer.Type, satisfaction) %>%
  summarise(counts = n())

# customer type by satisfaction and satisfaction level in each factors
cs_type_satisfaction_lvl_df <- airline_df[c(3,8:21,24)]
cs_type_satisfaction_lvl_df <- 
  cs_type_satisfaction_lvl_df %>% 
  pivot_longer(-c(Customer.Type, satisfaction),
               names_to = "factors",
               values_to = "satisfaction.level")  %>%
  group_by(Customer.Type, satisfaction, factors, satisfaction.level) %>%
  summarise(counts = n())
```
**Different perspectives from Customer Type**  

```{r echo = FALSE, warning = FALSE}
# customer type by type of travel and class
cs_type_travel_class_g <- 
  ggplot(cs_type_travel_class_df, 
         aes(x = Type.of.Travel,
             y = counts, 
             fill = Class)) + 
  geom_bar(stat='identity', position = "dodge") +
  labs(title = "Customer Type by Type of Travel and Class",
       x = "Type of Travel",
       y = "Frequency") + 
  theme(plot.title = element_text(hjust = 0.5)) +
  facet_wrap(~Customer.Type) +
  scale_fill_brewer(palette="Spectral")
cs_type_travel_class_g
```

* Both customers tend to choose the airline for business travel rather than personal travel, with a more distinct distribution of travel type in the disloyal customers group.  
* Disloyal customers prefer Eco class for business travel, while majority of loyal customers prefer Business class for business travel but Eco class for personal travel.

```{r echo = FALSE, warning = FALSE}
# customer type by gender and age
cs_type_gender_age_g <-
  ggplot(airline_df, 
         aes(x = Gender,
             y = Age,
             fill = Gender,
             color = Gender)) + 
  geom_violin(width = 0.3, position = position_dodge())+
  geom_boxplot(width = 0.1, color = "black", alpha = 0.2) +
  labs(title = "Customer Type by Gender and Age", 
       x = "Gender",
       y = "Age") + 
  theme(plot.title = element_text(hjust = 0.5)) +
  facet_wrap(~Customer.Type) +
  scale_fill_brewer(palette="Spectral")
cs_type_gender_age_g
```

* The distribution of age for gender in each customer type is similar.
* The distribution of age for loyal and disloyal customers is unalike; widely-spread age distribution for loyal customers and non-symmetric bimodal age distribution for disloyal customers, with larger distribution in mid 20's.
* The quartiles of the loyal customers fall between 30's to 50's, whereas the quartiles of disloyal customers are more concentrated at mid 20's to near 40's.
* Most disloyal customers are younger than loyal customers.

```{r include = FALSE, warning = FALSE}
# Not showing
# Flight distance by customer type and class
cs_type_flight_d_g <- 
  ggplot(airline_df, 
         aes(x = Flight.Distance,
             fill = Customer.Type)) +
  geom_density(alpha = 0.3) +
  labs(title = "Flight Distance by Customer Type and Class",
       y = "", 
       x = "Flight Distance") + 
  theme(plot.title = element_text(hjust = 0.5)) +
  guides(fill=guide_legend(title="Customer Type")) +
  facet_grid(Class ~ .) + 
  scale_fill_brewer(palette = "Spectral")
cs_type_flight_d_g
```

```{r echo = FALSE, warning = FALSE}
# Customer Type by satisfaction
cs_type_satisfaction_g <- 
  ggplot(cs_type_satisfaction_df, 
         aes(x = satisfaction,
             y = counts, 
             fill = satisfaction)) + 
  geom_bar(stat='identity', position = "dodge", width = 0.5) +
  guides(fill=guide_legend(title="Satisfaction")) +
  labs(title = "Satisfaction by Customer Type",
       x = "Satisfaction",
       y = "Frequency") + 
  theme(plot.title = element_text(hjust = 0.5)) +
  facet_wrap(~Customer.Type) +
  scale_fill_brewer(palette="Spectral")
cs_type_satisfaction_g
```

* No significant difference in the satisfaction level of each customer type.
* The number of customers whom satisfied with the service provided by the airline are slightly higher in each customer type group.

Since majority of the customers are loyal customers, hence we will focus on the ratings distribution of loyal customers. Looking into the distribution of ratings for loyal customers, most services have similar distribution of ratings in each customer type with gradually increase in the count from rating 1 to 4, peak at rating 4, and slight decrease in the rating count at rating 5. However, some services did not follow this pattern, such as ease of online booking, gate location and in-flight Wi-fi service, therefore we will focus on the distribution of ratings in these 3 services in the graphs below.

```{r echo = FALSE, warning = FALSE, fig.height = 7}
# Focus on three service type and only loyal customers
cs_type_ratings_df_focus <- 
  cs_type_ratings_df %>%
  filter((Customer.Type == "Loyal Customer") & 
           (services == "Gate.location" | 
            services == "Ease.of.Online.booking" |
            services == "Inflight.wifi.service"
            )
         )

# Ratings by customer type
cs_type_ratings_g <- 
  ggplot(cs_type_ratings_df_focus, 
         aes(x = ratings,
             y = counts, 
             fill = ratings)) + 
  geom_bar(stat='identity', position = "dodge") +
  labs(title = "Ratings in each services by customer type",
       x = "Ratings",
       y = "") + 
  theme(plot.title = element_text(hjust = 0.5)) +
  facet_grid(services ~ Customer.Type) +
  scale_fill_brewer(palette="Spectral")
cs_type_ratings_g
```

* It is observed that most customers rated 2 and 3 for ease of online booking and gate location service, and rated 3 for gate location service.
* This indicates that further investigation is required to examine the bad performance of online booking and gate location service, and immediate actions are required to improve the ratings for these two services.

### Type of Travel

**Different perspectives from Type of Travel**

```{r echo = FALSE, warning = FALSE}
# Type of Travel of Airline Passengers
# p_1 <- ggplot(airline_df, aes(Type.of.Travel, colour = Type.of.Travel, fill = Type.of.Travel)) + geom_bar(position = "dodge") + 
# labs(title = "Type of Travel", colour = "Type.of.Travel", y = "Number of Airline Passengers", x = "Type of Travel")+
# theme(axis.text = element_text(size = 5)) + theme(axis.title = element_text(size = 5)) + theme(plot.title = element_text(size = 7)) +
# theme(legend.text = element_text(size = 5))+ theme(legend.title = element_text(size = 5))+ theme(legend.key.height= unit(0.5, 'cm'),
# legend.key.width= unit(0.5, 'cm'))

p_2 <- ggplot(airline_df, aes(Type.of.Travel, colour = satisfaction, fill = satisfaction)) + geom_bar(position = "dodge") + 
  labs(title = "Satisfaction across Type of Travel", colour = "satisfaction", y = "Number of Airline Passengers", x = "Type of Travel")+ 
  theme(axis.text = element_text(size = 5)) + theme(axis.title = element_text(size = 5)) + theme(plot.title = element_text(size = 7)) +
  theme(legend.text = element_text(size = 5))+ theme(legend.title = element_text(size = 5))+ theme(legend.key.height= unit(0.5, 'cm'),
  legend.key.width= unit(0.5, 'cm')) 

# Gender across Type of Travel
# p_3 <- ggplot(airline_df, aes(Type.of.Travel, colour = Gender, fill = Gender)) + geom_bar(position = "dodge") + 
# labs(title = "Gender across Type of Travel", colour = "Gender", y = "Number of Airline Passengers", x = "Type of Travel")+ 
# theme(axis.text = element_text(size = 5)) + theme(axis.title = element_text(size = 5)) + theme(plot.title = element_text(size = 7)) +
# theme(legend.text = element_text(size = 5))+ theme(legend.title = element_text(size = 5))+ theme(legend.key.height= unit(0.5, 'cm'),
# legend.key.width= unit(0.5, 'cm')) 

# Customer.Type across Type of Travel
p_4 <- ggplot(airline_df, aes(Type.of.Travel, colour = Customer.Type, fill = Customer.Type)) + geom_bar(position = "dodge") + 
  labs(title = "Customer Type across Type of Travel", colour = "Customer.Type", y = "Number of Airline Passengers", x = "Type of Travel")+ 
  theme(axis.text = element_text(size = 5)) + theme(axis.title = element_text(size = 5)) + theme(plot.title = element_text(size = 7)) +
  theme(legend.text = element_text(size = 5))+ theme(legend.title = element_text(size = 5))+ theme(legend.key.height= unit(0.5, 'cm'),
  legend.key.width= unit(0.5, 'cm'))
  ggarrange(p_2, p_4, nrow = 2, ncol=1) 
```

* Business travelers tend to have a higher level of satisfaction and loyalty when compared to personal travelers. This could be due to a number of reasons such as the more comfortable and convenient travel arrangements offered by businesses to their employees, as well as the added perks and privileges that come with business travel such as upgrades and access to exclusive lounges.
* However, it's also worth noting that both types of travelers seem to have similar levels of dissatisfaction, raising concerns.

```{r echo = FALSE, warning = FALSE}
# Age across Type of Travel
p_5 <- ggplot(airline_df, aes(Age, colour = Type.of.Travel, fill = Type.of.Travel)) + geom_density(alpha = 0.5) + 
  labs(title = "Age across Type of Travel", colour = "Type.of.Travel", y = "Number of Airline Passengers", x = "Type of Travel")+ 
  theme(axis.text = element_text(size = 5)) + theme(axis.title = element_text(size = 5)) + theme(plot.title = element_text(size = 7)) +
  theme(legend.text = element_text(size = 5))+ theme(legend.title = element_text(size = 5))+ theme(legend.key.height= unit(0.5, 'cm'),
  legend.key.width= unit(0.5, 'cm')) 

# Flight Distance across Type of Travel
p_6 <- ggplot(airline_df,aes(x = Flight.Distance,fill = Type.of.Travel)) + geom_density(alpha = 0.5) + labs(title = "Flight Distance by Type of Travel",
       y = "Frequency", 
       x = "Flight Distance") +  guides(fill=guide_legend(title="Type.of.Travel")) +  theme(axis.text = element_text(size = 5)) + 
  theme(axis.title = element_text(size = 5)) + theme(plot.title = element_text(size = 7)) + theme(legend.text = element_text(size = 5))+
  theme(legend.title = element_text(size = 5))+ theme(legend.key.height= unit(0.5, 'cm'), legend.key.width= unit(0.5, 'cm'))
 
ggarrange(p_5, p_6, nrow = 2, ncol=1) 
```

* Business travelers tend to be older and have longer flight distances than personal travelers. This could be due to a number of factors such as the nature of their work requiring more frequent and longer-distance travel, or the fact that older individuals may be more likely to hold positions that involve traveling for business. 
* Additionally, business travelers may also have a higher disposable income and be more likely to upgrade to premium seating or business class, which can result in longer flight distances. 
* Furthermore, older travelers may also prefer longer flights as they offer more comfort and amenities.

```{r echo = FALSE, warning = FALSE}

# Services
# Inflight.wifi.service across Type of Travel

p_7 <- ggplot(airline_df, aes(Inflight.wifi.service, colour = Type.of.Travel, fill = Type.of.Travel)) + geom_bar(position = "dodge") + 
  labs(title = "Inflight wifi service across Type of Travel", colour = "Type.of.Travel", y = "Number of Airline Passengers", x = "Rating")+ 
  theme(axis.text = element_text(size = 5)) +  theme(axis.title = element_text(size = 5)) + theme(plot.title = element_text(size = 7)) +
  theme(legend.text = element_text(size = 5))+ theme(legend.title = element_text(size = 5))+ theme(legend.key.height= unit(0.5, 'cm'),
  legend.key.width= unit(0.5, 'cm')) 

# Departure.Arrival.time.convenient across Type of Travel

p_8 <- ggplot(airline_df, aes(Departure.Arrival.time.convenient, colour = Type.of.Travel, fill = Type.of.Travel)) + geom_bar(position = "dodge") + 
  labs(title = "Departure Arrival time convenient across Type of Travel", colour = "Type.of.Travel", y = "Number of Airline Passengers", x = "Rating")+ 
  theme(axis.text = element_text(size = 5)) +  theme(axis.title = element_text(size = 5)) + theme(plot.title = element_text(size = 7)) +
  theme(legend.text = element_text(size = 5))+ theme(legend.title = element_text(size = 5))+ theme(legend.key.height= unit(0.5, 'cm'),
  legend.key.width= unit(0.5, 'cm')) 

# Ease.of.Online.booking across Type of Travel
p_9 <- ggplot(airline_df, aes(Ease.of.Online.booking, colour = Type.of.Travel, fill = Type.of.Travel)) + geom_bar(position = "dodge") + 
  labs(title = "Ease of Online booking across Type of Travel", colour = "Type.of.Travel", y = "Number of Airline Passengers", x = "Rating")+ 
  theme(axis.text = element_text(size = 5)) +  theme(axis.title = element_text(size = 5)) + theme(plot.title = element_text(size = 7)) +
  theme(legend.text = element_text(size = 5))+ theme(legend.title = element_text(size = 5))+ theme(legend.key.height= unit(0.5, 'cm'),
  legend.key.width= unit(0.5, 'cm')) 

# Gate.location across Type of Travel
p_10 <- ggplot(airline_df, aes(Gate.location, colour = Type.of.Travel, fill = Type.of.Travel)) + geom_bar(position = "dodge") + 
  labs(title = "Gate location across Type of Travel", colour = "Type.of.Travel", y = "Number of Airline Passengers", x = "Rating")+ 
  theme(axis.text = element_text(size = 5)) +  theme(axis.title = element_text(size = 5)) + theme(plot.title = element_text(size = 7)) +
  theme(legend.text = element_text(size = 5))+ theme(legend.title = element_text(size = 5))+ theme(legend.key.height= unit(0.5, 'cm'),
  legend.key.width= unit(0.5, 'cm')) 

# Online.boarding across Type of Travel
p_11 <- ggplot(airline_df, aes(Online.boarding, colour = Type.of.Travel, fill = Type.of.Travel)) + geom_bar(position = "dodge") + 
  labs(title = "Online boarding across Type of Travel", colour = "Type.of.Travel", y = "Number of Airline Passengers", x = "Rating")+ 
  theme(axis.text = element_text(size = 5)) +  theme(axis.title = element_text(size = 5)) + theme(plot.title = element_text(size = 7)) +
  theme(legend.text = element_text(size = 5))+ theme(legend.title = element_text(size = 5))+ theme(legend.key.height= unit(0.5, 'cm'),
  legend.key.width= unit(0.5, 'cm')) 

# Seat.comfort across Type of Travel
p_12 <- ggplot(airline_df, aes(Seat.comfort, colour = Type.of.Travel, fill = Type.of.Travel)) + geom_bar(position = "dodge") + 
  labs(title = "Seat comfort across Type of Travel", colour = "Type.of.Travel", y = "Number of Airline Passengers", x = "Rating")+ 
  theme(axis.text = element_text(size = 5)) +  theme(axis.title = element_text(size = 5)) + theme(plot.title = element_text(size = 7)) +
  theme(legend.text = element_text(size = 5))+ theme(legend.title = element_text(size = 5))+ theme(legend.key.height= unit(0.5, 'cm'),
  legend.key.width= unit(0.5, 'cm')) 

# Inflight.entertainment across Type of Travel
p_13 <- ggplot(airline_df, aes(Inflight.entertainment, colour = Type.of.Travel, fill = Type.of.Travel)) + geom_bar(position = "dodge") + 
  labs(title = "Inflight entertainment across Type of Travel", colour = "Type.of.Travel", y = "Number of Airline Passengers", x = "Rating")+ 
  theme(axis.text = element_text(size = 5)) +  theme(axis.title = element_text(size = 5)) + theme(plot.title = element_text(size = 7)) +
  theme(legend.text = element_text(size = 5))+ theme(legend.title = element_text(size = 5))+ theme(legend.key.height= unit(0.5, 'cm'),
  legend.key.width= unit(0.5, 'cm')) 

# On.board.service across Type of Travel
p_14 <- ggplot(airline_df, aes(On.board.service, colour = Type.of.Travel, fill = Type.of.Travel)) + geom_bar(position = "dodge") + 
  labs(title = "On board service across Type of Travel", colour = "Type.of.Travel", y = "Number of Airline Passengers", x = "Rating")+ 
  theme(axis.text = element_text(size = 5)) +  theme(axis.title = element_text(size = 5)) + theme(plot.title = element_text(size = 7)) +
  theme(legend.text = element_text(size = 5))+ theme(legend.title = element_text(size = 5))+ theme(legend.key.height= unit(0.5, 'cm'),
  legend.key.width= unit(0.5, 'cm')) 

# Leg.room.service across Type of Travel
p_15 <- ggplot(airline_df, aes(Leg.room.service, colour = Type.of.Travel, fill = Type.of.Travel)) + geom_bar(position = "dodge") + 
  labs(title = "Leg room service across Type of Travel", colour = "Type.of.Travel", y = "Number of Airline Passengers", x = "Rating")+ 
  theme(axis.text = element_text(size = 5)) +  theme(axis.title = element_text(size = 5)) + theme(plot.title = element_text(size = 7)) +
  theme(legend.text = element_text(size = 5))+ theme(legend.title = element_text(size = 5))+ theme(legend.key.height= unit(0.5, 'cm'),
  legend.key.width= unit(0.5, 'cm')) 

# Baggage.handling across Type of Travel
p_16 <- ggplot(airline_df, aes(Baggage.handling, colour = Type.of.Travel, fill = Type.of.Travel)) + geom_bar(position = "dodge") + 
  labs(title = "Baggage handling across Type of Travel", colour = "Type.of.Travel", y = "Number of Airline Passengers", x = "Rating")+ 
  theme(axis.text = element_text(size = 5)) +  theme(axis.title = element_text(size = 5)) + theme(plot.title = element_text(size = 7)) +
  theme(legend.text = element_text(size = 5))+ theme(legend.title = element_text(size = 5))+ theme(legend.key.height= unit(0.5, 'cm'),
  legend.key.width= unit(0.5, 'cm')) 

# Checkin.service across Type of Travel
p_17 <- ggplot(airline_df, aes(Checkin.service, colour = Type.of.Travel, fill = Type.of.Travel)) + geom_bar(position = "dodge") + 
  labs(title = "Checking service across Type of Travel", colour = "Type.of.Travel", y = "Number of Airline Passengers", x = "Rating")+ 
  theme(axis.text = element_text(size = 5)) +  theme(axis.title = element_text(size = 5)) + theme(plot.title = element_text(size = 7)) +
  theme(legend.text = element_text(size = 5))+ theme(legend.title = element_text(size = 5))+ theme(legend.key.height= unit(0.5, 'cm'),
  legend.key.width= unit(0.5, 'cm')) 

# Inflight.service across Type of Travel
p_18 <- ggplot(airline_df, aes(Inflight.service, colour = Type.of.Travel, fill = Type.of.Travel)) + geom_bar(position = "dodge") + 
  labs(title = "Inflight service across Type of Travel", colour = "Type.of.Travel", y = "Number of Airline Passengers", x = "Rating")+ 
  theme(axis.text = element_text(size = 5)) +  theme(axis.title = element_text(size = 5)) + theme(plot.title = element_text(size = 7)) +
  theme(legend.text = element_text(size = 5))+ theme(legend.title = element_text(size = 5))+ theme(legend.key.height= unit(0.5, 'cm'),
  legend.key.width= unit(0.5, 'cm')) 

# Cleanliness across Type of Travel
p_19 <- ggplot(airline_df, aes(Cleanliness, colour = Type.of.Travel, fill = Type.of.Travel)) + geom_bar(position = "dodge") + 
  labs(title = "Cleanliness across Type of Travel", colour = "Type.of.Travel", y = "Number of Airline Passengers", x = "Rating")+ 
  theme(axis.text = element_text(size = 5)) +  theme(axis.title = element_text(size = 5)) + theme(plot.title = element_text(size = 7)) +
  theme(legend.text = element_text(size = 5))+ theme(legend.title = element_text(size = 5))+ theme(legend.key.height= unit(0.5, 'cm'),
  legend.key.width= unit(0.5, 'cm')) 
```

```{r echo = FALSE, warning = FALSE}
ggarrange(p_7, p_8, p_9, p_10, nrow = 2, ncol=2)
ggarrange(p_15, p_16, p_17, p_18, nrow = 2, ncol=2)
ggarrange(p_15, p_16, p_17, p_18, nrow = 2, ncol=2)
```

* From the perspective of "Type of Travel," it is advised that Airlines should give more attention to the four services such as "**In-flight Wi-fi service**", "**Ease of Online Booking**", "**Departure Arrival time convenient**" and "**Gate location**" as they are identified to be major sources of dissatisfaction among business travelers. 
* By identifying and addressing these specific areas, Airlines can take effective measures to improve the overall travel experience for their customers, resulting in increased satisfaction and loyalty.

* On the other hand, when it comes to Personal Travel, the service of "**Departure Arrival Time Convenience**" receives significant high ratings and the other services still have a significant potential to improve as majority of the ratings for those services fall between "1" and "3" which indicates that those services are not performing as well as they could. 
* By taking initiative to improve these services, the ratings could be increased from "1" to "3" to "3" to "5", indicating a significant increase in passenger satisfaction and loyalty.  

### Class
**Different perspectives from Flight Class**

```{r echo = FALSE, warning = FALSE}

# Class of Airline Passengers
class_1 <- ggplot(airline_df, aes(Class, colour = Class, fill = Class)) + geom_bar()+
  labs(title = "Class of Airline Passengers") + 
  theme(axis.text = element_text(size = 5)) + 
  theme(axis.title = element_text(size = 5)) +
  theme(plot.title = element_text(size = 5)) +
  theme(legend.text = element_text(size = 5))+
  theme(legend.title = element_text(size = 5))

# Satisfaction across Class
class_2 <- ggplot(airline_df, aes(Class, colour = satisfaction, fill = satisfaction)) + geom_bar(position = "dodge") + 
  labs(title = "Satisfaction across Class", colour = "satisfaction")+ 
  theme(axis.text = element_text(size = 5)) + 
  theme(axis.title = element_text(size = 5)) +
  theme(plot.title = element_text(size = 5)) +
  theme(legend.text = element_text(size = 5))+
  theme(legend.title = element_text(size = 5))

# Gender across Class
class_3 <- ggplot(airline_df, aes(Class, colour = Gender, fill = Gender)) + geom_bar(position = "dodge") + 
  labs(title = "Gender across Class", colour = "Gender")+ 
  theme(axis.text = element_text(size = 5)) + 
  theme(axis.title = element_text(size = 5)) +
  theme(plot.title = element_text(size = 5)) +
  theme(legend.text = element_text(size = 5))+
  theme(legend.title = element_text(size = 5))

# Customer.Type across Class
class_4 <- ggplot(airline_df, aes(Class, colour = Customer.Type, fill = Customer.Type)) + geom_bar(position = "dodge") + 
  labs(title = "Customer.Type across Class", colour = "Customer.Type")+ 
  theme(axis.text = element_text(size = 5)) + 
  theme(axis.title = element_text(size = 5)) +
  theme(plot.title = element_text(size = 5)) +
  theme(legend.text = element_text(size = 5))+
  theme(legend.title = element_text(size = 5))

# Age across Class
class_5 <- ggplot(airline_df, aes(Age, colour = Class, fill = Class)) + geom_density(alpha = 0.5) + 
  labs(title = "Age across Class")+ 
  theme(axis.text = element_text(size = 5)) + 
  theme(axis.title = element_text(size = 5)) +
  theme(plot.title = element_text(size = 5)) +
  theme(legend.text = element_text(size = 5))+
  theme(legend.title = element_text(size = 5))

# Flight Distance across Class
class_6 <- ggplot(airline_df,aes(x = Flight.Distance,fill = Class)) +
  geom_density(alpha = 0.5) +
  labs(title = "Flight Distance by Class",
       y = "Frequency", 
       x = "Flight Distance") + 
  guides(fill=guide_legend(title="Class")) + 
  theme(axis.text = element_text(size = 5)) + 
  theme(axis.title = element_text(size = 5)) +
  theme(plot.title = element_text(size = 5)) +
  theme(legend.text = element_text(size = 5))+
  theme(legend.title = element_text(size = 5))

# Inflight.wifi.service across Class
class_7 <- ggplot(airline_df, aes(Inflight.wifi.service, colour = Class, fill = Class)) + geom_bar(position = "dodge") + 
  labs(title = "Inflight.wifi.service across Class")+ 
  theme(axis.text = element_text(size = 5)) + 
  theme(axis.title = element_text(size = 5)) +
  theme(plot.title = element_text(size = 5)) +
  theme(legend.text = element_text(size = 5))+
  theme(legend.title = element_text(size = 5))

# Departure.Arrival.time.convenient across Class
class_8 <- ggplot(airline_df, aes(Departure.Arrival.time.convenient, colour = Class, fill = Class)) + geom_bar(position = "dodge") + 
  labs(title = "Departure.Arrival.time.convenient across Class")+ 
  theme(axis.text = element_text(size = 5)) + 
  theme(axis.title = element_text(size = 5)) +
  theme(plot.title = element_text(size = 5)) +
  theme(legend.text = element_text(size = 5))+
  theme(legend.title = element_text(size = 5))

# Ease.of.Online.booking across Class
class_9 <- ggplot(airline_df, aes(Ease.of.Online.booking, colour = Class, fill = Class)) + geom_bar(position = "dodge") + 
  labs(title = "Ease.of.Online.booking across Class")+ 
  theme(axis.text = element_text(size = 5)) + 
  theme(axis.title = element_text(size = 5)) +
  theme(plot.title = element_text(size = 5)) +
  theme(legend.text = element_text(size = 5))+
  theme(legend.title = element_text(size = 5))

# Gate.location across Class
class_10 <- ggplot(airline_df, aes(Gate.location, colour = Class, fill = Class)) + geom_bar(position = "dodge") + 
  labs(title = "Gate.location across Class")+ 
  theme(axis.text = element_text(size = 5)) + 
  theme(axis.title = element_text(size = 5)) +
  theme(plot.title = element_text(size = 5)) +
  theme(legend.text = element_text(size = 5))+
  theme(legend.title = element_text(size = 5))

# Online.boarding across Class
class_11 <- ggplot(airline_df, aes(Online.boarding, colour = Class, fill = Class)) + geom_bar(position = "dodge") + 
  labs(title = "Online.boarding across Class")+ 
  theme(axis.text = element_text(size = 5)) + 
  theme(axis.title = element_text(size = 5)) +
  theme(plot.title = element_text(size = 5)) +
  theme(legend.text = element_text(size = 5))+
  theme(legend.title = element_text(size = 5))

# Seat.comfort across Class
class_12 <- ggplot(airline_df, aes(Seat.comfort, colour = Class, fill = Class)) + geom_bar(position = "dodge") + 
  labs(title = "Seat.comfort across Class")+ 
  theme(axis.text = element_text(size = 5)) + 
  theme(axis.title = element_text(size = 5)) +
  theme(plot.title = element_text(size = 5)) +
  theme(legend.text = element_text(size = 5))+
  theme(legend.title = element_text(size = 5))

# Inflight.entertainment across Class
class_13 <- ggplot(airline_df, aes(Inflight.entertainment, colour = Class, fill = Class)) + geom_bar(position = "dodge") + 
  labs(title = "Inflight.entertainment across Class")+ 
  theme(axis.text = element_text(size = 5)) + 
  theme(axis.title = element_text(size = 5)) +
  theme(plot.title = element_text(size = 5)) +
  theme(legend.text = element_text(size = 5))+
  theme(legend.title = element_text(size = 5))

# On.board.service across Class
class_14 <- ggplot(airline_df, aes(On.board.service, colour = Class, fill = Class)) + geom_bar(position = "dodge") + 
  labs(title = "On.board.service across Class")+ 
  theme(axis.text = element_text(size = 5)) + 
  theme(axis.title = element_text(size = 5)) +
  theme(plot.title = element_text(size = 5)) +
  theme(legend.text = element_text(size = 5))+
  theme(legend.title = element_text(size = 5))

# Leg.room.service across Class
class_15 <- ggplot(airline_df, aes(Leg.room.service, colour = Class, fill = Class)) + geom_bar(position = "dodge") + 
  labs(title = "Leg.room.service across Class")+ 
  theme(axis.text = element_text(size = 5)) + 
  theme(axis.title = element_text(size = 5)) +
  theme(plot.title = element_text(size = 5)) +
  theme(legend.text = element_text(size = 5))+
  theme(legend.title = element_text(size = 5))

# Baggage.handling across Class
class_16 <- ggplot(airline_df, aes(Baggage.handling, colour = Class, fill = Class)) + geom_bar(position = "dodge") + 
  labs(title = "Baggage.handling across Class")+ 
  theme(axis.text = element_text(size = 5)) + 
  theme(axis.title = element_text(size = 5)) +
  theme(plot.title = element_text(size = 5)) +
  theme(legend.text = element_text(size = 5))+
  theme(legend.title = element_text(size = 5))

# Checkin.service across Class
class_17 <- ggplot(airline_df, aes(Checkin.service, colour = Class, fill = Class)) + geom_bar(position = "dodge") + 
  labs(title = "Checkin.service across Class")+ 
  theme(axis.text = element_text(size = 5)) + 
  theme(axis.title = element_text(size = 5)) +
  theme(plot.title = element_text(size = 5)) +
  theme(legend.text = element_text(size = 5))+
  theme(legend.title = element_text(size = 5))

# Inflight.service across Class
class_18 <- ggplot(airline_df, aes(Inflight.service, colour = Class, fill = Class)) + geom_bar(position = "dodge") + 
  labs(title = "Inflight.service across Class")+ 
  theme(axis.text = element_text(size = 5)) + 
  theme(axis.title = element_text(size = 5)) +
  theme(plot.title = element_text(size = 5)) +
  theme(legend.text = element_text(size = 5))+
  theme(legend.title = element_text(size = 5))

# Cleanliness across Class
class_19 <- ggplot(airline_df, aes(Cleanliness, colour = Class, fill = Class)) + geom_bar(position = "dodge") + 
  labs(title = "Cleanliness across Class")+ 
  theme(axis.text = element_text(size = 5)) + 
  theme(axis.title = element_text(size = 5)) +
  theme(plot.title = element_text(size = 5)) +
  theme(legend.text = element_text(size = 5))+
  theme(legend.title = element_text(size = 5))
  
# Type of Travel across Class
class_20 <- ggplot(airline_df, aes(Type.of.Travel, colour = Class, fill = Class)) + geom_bar(position = "dodge") +
labs(title = "Type.of.Travel across Class") +
theme(axis.text = element_text(size = 5)) +
theme(axis.title = element_text(size = 5)) +
theme(plot.title = element_text(size = 5)) +
theme(legend.text = element_text(size = 5)) +
theme(legend.title = element_text(size = 5))
```

```{r echo = FALSE, warning = FALSE, fig.height = 4}
ggarrange(class_1, class_3, ncol=2)
```

* The distribution of passengers between business and economy class is roughly equal, with a nearly equal number of male and female passengers in both classes.

```{r echo = FALSE, warning = FALSE, fig.height = 4}
class_4
```

* In addition, the customer demographic in both business and economy class is similar, with the majority of passengers being Loyal Customers and a small percentage being Disloyal Customers.

```{r echo = FALSE, warning = FALSE, fig.height = 4}
class_5
```

* In economy class, there is a higher proportion of passengers aged below 30 and between 60 to 70 years old, whereas in business class, there is a higher proportion of passengers aged between 30 to 60 years old. The demographic differences between economy and business class passengers could be due to various factors such as pricing, travel purpose, life stage and perception of comfort.

* Younger passengers might choose Eco class due to cost concerns, as it is typically the most affordable option. They might also be more likely to be traveling for leisure or personal reasons rather than for work, leading them to prioritize cost savings over amenities. Alternatively, younger passengers might prioritize other aspects of their trip, such as destination or duration, and choose the Eco class in order to allocate more of their budget to those factors.

* Business class is often chosen by adults for the enhanced comfort it provides, such as more spacious seating and additional amenities. It may also be preferred for the convenience it offers, including priority services at the airport and access to exclusive lounges. The ability to work or relax in a more comfortable setting during long flights can also be a factor in the choice of business class. Additionally, some adults may be attracted to the prestige associated with flying in this class.

```{r echo = FALSE, warning = FALSE, fig.height = 4}
class_20
```

* According to the graph, a significant number of business class passengers are traveling for business purposes. While the Eco class also has a proportion of business travelers, there is a slightly higher percentage of passengers traveling for personal reasons.

```{r echo = FALSE, warning = FALSE, fig.height = 4}
class_6
```

* From the graph, we can see that passengers often choose business class for further flights. It may because of the added comfort and amenities on long flights.

```{r echo = FALSE, warning = FALSE, fig.height = 4}
class_2
```

* Passengers in the business class are generally happy with the airline's services, but there is still room for improvement. On the other hand, many passengers in the economy classes were not satisfied or were neutral about the services they received. To make sure that all passengers have a good experience, it is important to focus on improving the services provided to the economy and economy plus classes.

**(Pending RACHMAT's interpretation)**

```{r echo = FALSE, warning = FALSE}
ggarrange(class_7, class_8, class_9, class_10, nrow = 2, ncol=2)
ggarrange(class_11, class_12, class_13, class_14, nrow = 2, ncol=2)
ggarrange(class_15, class_16, class_17, class_18, nrow = 2, ncol=2)
```
* From the graphs presented above, the areas that generate the most dissatisfaction among passengers for both business class and economy class are inflight wifi service, ease of online booking, gate location, and food and drink. To enhance the passenger experience and improve the airline's image and values, these areas require improvement.
* Furthermore, for economy class, additional areas such as seat comfort, inflight entertainment, on-board service, leg room, check-in service, and cleanliness also need attention as they frequently receive low ratings and affect the overall passenger experience.

## Classification
Classification is the process of predicting the target label based on features in the dataset. In this project, we will build classification model using different algorithms to predict the satisfaction of customers (either satisfied or neutral/dissatisfied) based on available features such as customer demographics, flight details, service ratings etc. 

### Handle Categorical Data
Convert categorical data to numerical data using:  
**Ordinal Data**  
Convert Ordinal to Integer
```{r echo = TRUE, warning = FALSE}
airline_df_m <- airline_df
ord_ratings <- c("Inflight.wifi.service", "Food.and.drink", "Seat.comfort",
          "Departure.Arrival.time.convenient",	"Ease.of.Online.booking",
          "Gate.location", "Online.boarding", "Inflight.entertainment",
          "On.board.service",	"Leg.room.service",	"Baggage.handling",
          "Checkin.service",	"Inflight.service",	"Cleanliness"
          )
airline_df_m[ord_ratings] <- 
  lapply(airline_df_m[ord_ratings], 
         function(x) as.numeric(as.character(x))
         )
```
**Nominal Data**  
One-hot encoding to convert each category into a new column and assign a value as 1 or 0 to the column
```{r echo = TRUE, warning = FALSE}
# One-Hot encoding
features <- c("Gender",	"Customer.Type",	"Age", "Type.of.Travel", "Class",	
              "Flight.Distance", ord_ratings, "Departure.Delay.in.Minutes",
              "Arrival.Delay.in.Minutes")
airline_df_m_trsf <- 
  cbind(data.frame(predict(dummyVars(
          ~.,
          data = airline_df_m),
          airline_df_m)
          ), 
        satisfaction = airline_df_m$satisfaction
        )
airline_df_m_trsf <- subset(airline_df_m_trsf, 
                            select = -c(satisfaction.neutral.or.dissatisfied,
                                        satisfaction.satisfied, id))

# Remove perfectly correlated variables
airline_df_m_trsf <- subset(airline_df_m_trsf, 
                            select = -c(Gender.Male, Customer.Type.Loyal.Customer, 
                                        Type.of.Travel.Personal.Travel, Class.Eco))

# Set satisfaction as factors
airline_df_m_trsf$satisfaction <- factor(airline_df_m_trsf$satisfaction)
```

### Correlation
Further investigation on the correlation between different airline services and overall satisfaction.
```{r echo = TRUE, warning = FALSE}

#Correlation between different variables
#Removed the non-numeric data
# airline_corr<- airline_df %>%
#   select(!c('id','Gender', 'Customer.Type',	'Age', 'Type.of.Travel',	'Class',	'Flight.Distance',)) %>%   mutate_if(is.factor,as.numeric) 
# 
# 
# # Creating correlation matrix
# corr_mat <- round(cor(airline_corr),2)
# head(corr_mat)
# 
# # reduce the size of correlation matrix
# melted_corr_mat <- melt(corr_mat)
# head(melted_corr_mat)
 
# plotting the correlation heatmap
# library(ggplot2)
# ggplot(data = melted_corr_mat, aes(x=Var1, y=Var2, fill=value)) + geom_tile() +
#   geom_text(aes(Var2, Var1, label = value), color = "black", size = 4)
# 
# ggcorrplot::ggcorrplot(corr_mat, hc.order = TRUE, type = "lower",
#    lab = TRUE)

#Included categorical data in correlation heatmap
# airline_corr2<- airline_df %>%
#   select(!c('id')) %>%   mutate_if(is.factor,as.numeric) 
# airline_corr2<- airline_corr2 %>%
#   select(everything()) %>%   mutate_if(is.integer,as.numeric) 
# str(airline_corr2)

#Creating correlation matrix

# corr_mat2 <- round(cor(airline_corr2),2)
# head(corr_mat2)
# 
# # reduce the size of correlation matrix
# melted_corr_mat2 <- melt(corr_mat2)
# head(melted_corr_mat2)
 
## plotting the correlation heatmap
#  library(ggplot2) 
#  ggplot(data = melted_corr_mat, aes(x=Var1, y=Var2, 
#                                    fill=value)) + 
#  geom_tile() + 
#  geom_text(aes(Var2, Var1, label = value), 
#            color = "black", size = 4) 

# ggcorrplot::ggcorrplot(corr_mat2, hc.order = TRUE, type = "lower",
#    lab = TRUE)
```   

### Data Splitting
Data is split into train and test dataset (80:20), 82,258 and 21,646 records respectively.
```{r echo = TRUE, warning = FALSE}
# Splitting dataset
split <- sample.split(airline_df_m_trsf, SplitRatio = 0.8)
train <- subset(airline_df_m_trsf, split == "TRUE")
test <- subset(airline_df_m_trsf, split == "FALSE")
```

We will build the classification model using several classifiers, which is Logistic Regression, Decision Trees and K-Nearest Neighbors (KNN), then evaluate, discuss and compare the results accordingly.

### Logistic Regression
Logistic Regression is a regression algorithm that predicts the value of target variable (dependent variable) by investigating the relationship between the independent variable and the dependent variable. There are few important assumptions for regression, which is appropriate outcome structure, observations independence, little or no multicollinearity among the independent variables, linearity of independent variables and log odds and large sample size.  

Fit logistic regression model using the glm (generalized linear model) function  
**Model Summary:**
```{r echo = TRUE, warning = FALSE}
logit_model <- glm(satisfaction ~.,
                   family = binomial(link='logit'),
                   data = train)
summary(logit_model)
```

* Most of the predictors are statistically significant to the customer satisfaction (p < 0.05), except Gender and Flight Distance.
* Looking at the null and residual deviance, it is shown that the difference between these two deviance is huge, thus can conclude that the model is a good fit. 

**Model Prediction & Evaluation**    
Model evaluation using confusion matrix
```{r echo = TRUE, warning = FALSE}
# Predict test data
predict_reg <- predict(logit_model, 
                       subset(test, 
                              select = -c(satisfaction)
                              ),
                       type = "response")
predict_reg <- ifelse(predict_reg >0.5, "satisfied", "neutral or dissatisfied")

# Confusion matrix
confusionMatrix(factor(predict_reg), test$satisfaction)
```

* Based on the confusion matrix, it is observed that the accuracy of the model is high with roughly 88%, and the accuracy is much higher than the no information rate (percentage of the data with the majority class). 
* The model also shows high sensitivity and specificity, which means it can correctly predict the customer satisfaction, and only less than 17% of the customers satisfaction are wrongly predicted.
* The Kappa statistic is around 0.75, indicate excellent agreement between individuals.

### Decision Tree
Build the decision tree model using ctree
```{r echo = TRUE, warning = FALSE}
dt_model <- ctree(satisfaction ~ ., train)
# plot(dt_model)
```

**Model Prediction & Evaluation**    
Model evaluation using confusion matrix
```{r echo = TRUE, warning = FALSE}
# Predict test data
predict_dt <- predict(dt_model, test)

# Confusion matrix
dt_m <- table(test$satisfaction, predict_dt)
dt_m
dt_ac <- sum(diag(dt_m)) / sum(dt_m)
print(paste('Accuracy =', dt_ac))
```

### K-Nearest Neighbour (KNN)

The K-Nearest Neighbors (KNN) algorithm is a simple, yet powerful, supervised machine learning algorithm. It is used for both classification and regression problems. In classification, the idea is to find the k-number of nearest data points in the training set for a new data point, and then predict the class of the new data point based on the majority class among its k-nearest neighbors.

Fit the KNN model

* Scaling the features is carried to ensures that all features are on the same scale, so that one feature does not dominate the distance measure.

* The square root of the total number of observations is commonly used to determine the optimal k value as it balances the trade-off between overfitting and underfitting. Overfitting occurs when a model is too complex and is fitting the noise in the training data, while underfitting occurs when a model is too simple and is not fitting the training data well. 

* After running the code, it shows that k value is approximate 286.808298345777 and k value 286 & 287 are further being chosen for our model prediction.

```{r echo = TRUE, warning = FALSE}
# Feature scaling
# Normalize the range of independent variables or features of data
train_scale <- scale(train[, 1:22])
test_scale <- scale(test[, 1:22])

# Determine the optimal k value using square root of total observations
# sqrt(NROW(train))
# 285.1596

# KNN (try 285, 286)
knn_model_285 <- knn(train = train_scale,
                     test = test_scale,
                     cl = train$satisfaction,
                     k = 285)
knn_model_286 <- knn(train = train_scale,
                     test = test_scale,
                     cl = train$satisfaction,
                     k = 286)
```

**Model Prediction & Evaluation**    
Model evaluation using confusion matrix

```{r echo = TRUE, warning = FALSE}
# Confusion Matrix
confusionMatrix(knn_model_285, test$satisfaction)
confusionMatrix(knn_model_286, test$satisfaction)
```

* The result shows that the accuracy of the KNN model is 90.6% for k = 285 and 90.5% for k = 286. 
* The accuracy is quite high, which means that the model is performing well and making correct predictions for a high percentage of the test data. (Generally, an accuracy of 90% or higher is considered to be very good.)

* The confusion matrix results indicate that the KNN model with k = 285 and k = 286 have a high accuracy of around 90%, and good sensitivity and specificity. 
* The model is able to correctly predict the majority of the test data points and it may have slightly better performance with k = 285, but the difference is very small.

* In order to further improve the KNN model, we proceed to find the optimal k value.

```{r echo = TRUE, warning = FALSE}
# Improve model and find optimal k value
# i = 1
# k.optm = 1
# for (i in 1:25){ 
#     knn <-  knn(train = train_scale, 
#                 test = test_scale, 
#                 cl = train$satisfaction, 
#                 k = i)
#     k.optm[i] <- 100 * sum(test$satisfaction == knn)/NROW(test)
#     k = i
#     cat(k, '=', k.optm[i], '\n')
# }
# 1 = 91.39795 
# 2 = 91.00065 
# 3 = 92.69611 
# 4 = 92.39582 
# 5 = 92.86242 
# 6 = 92.72845 
# 7 = 92.99185 
# 8 = 92.73769 
# 9 = 92.83932 
# 10 = 92.8578 
# 11 = 92.89014 
# 12 = 92.8116 
# 13 = 92.91324 
# 14 = 92.86704 
# 15 = 92.71921 
# 16 = 92.64529 
# 17 = 92.64529 
# 18 = 92.56214 
# 19 = 92.64529 
# 20 = 92.66839 
# 21 = 92.58062 
# 22 = 92.4836 
# 23 = 92.51132 
# 24 = 92.43278 
# 25 = 92.46974 
# plot(k.optm, type="b", xlab="K- Value", ylab="Accuracy level")

# Optimal k: 7

# KNN (use 7)
knn_model_7 <- knn(train = train_scale,
                    test = test_scale,
                    cl = train$satisfaction,
                    k = 7)

# Confusion Matrix
confusionMatrix(knn_model_7, test$satisfaction)
```

* From the output, it can be seen that the highest accuracy is 93% when k = 7, which means that when k = 7, the model correctly predicted the class for 93% of the test samples. Therefore, 7 is the optimal k value for this model.

# Results
Which model works the best? Justify. 


# Conclusion
Summarize the EDA part and model part. Airline of which class need to focus on what services?


<<<<<<< Updated upstream
* From the perspective of "Type of Travel," it is advised that Airlines should give more attention to the four services such as "In-flight wifi service," "Ease of Online Booking," "Departure Arrival time convenient," and "Gate location" as they are identified to be major sources of dissatisfaction among business travelers. 

=======
* From the perspective of "Type of Travel," it is advised that Airlines should give more attention to the four services such as "In-flight Wi-Fi service," "Ease of Online Booking," "Departure Arrival time convenient," and "Gate location" as they are identified to be major sources of dissatisfaction among business travelers. 
>>>>>>> Stashed changes
* For Personal Travel, the majority of the ratings for these services fall between "1" and "3" which indicates that these services are not performing as well as they could. By taking initiative to improve these services, the ratings could be increased from "1" to "3" to "3" to "5", indicating a significant increase in passenger satisfaction and loyalty. 

# Contribution

# Reference
